### 2018-03-22 morus.tex
added approximations
linear approximation fragments...

\begin{figure}
  \substatesfalse
  % \substatesfalse to label state words and/or masks
  \centering
  \begin{tikzpicture}[xscale=1.0,yscale=1.5]%{{{
  \ifsubstates \pgfmathsetmacro{\roundsep}{1.25}
  \else        \pgfmathsetmacro{\roundsep}{0.80} \fi
  \pgfmathsetmacro{\opoffset}{.1}

@@

    \foreach \w in {0,...,4} {
      \ifthenelse{\equal{\w}{\r}}{
        \draw (W\rprev\w) -- (xnd\r);
        \draw (lll\r) -- (W\r\w);
      }{
        \draw (W\rprev\w) -- (W\r\w);
      }
    }
  }
  \end{tikzpicture}%}}}
  \caption{\cipher{MiniMorus} state update function (1 step = 5 rounds).}
  \label{fig:minimorus}
\end{figure}

\end{document}

>>>>

\noindent
2 approximations for $S^{2,2}_{0}$:
\begin{align*}
  S^{2,2}_0 &= C^0_{27} \oplus C^1_{0, 8, 26} \oplus C^2_{7,13,31} \oplus C^3_{12} \tag{corr. $2^{-7}$} \\
  S^{2,2}_0 &= C^1_{2} \oplus C^2_{1,7,15,27} \oplus C^3_{6,14,20} \oplus
  C^4_{19} \tag{corr. $2^{-9}$} \\
\intertext{Combined ciphertext-only approximation:}
  0 &= C^0_{27} \oplus C^1_{0, 2, 26, 8} \oplus C^2_{1,13,15,27,31} \oplus
  C^3_{6,12,14,20} \oplus C^4_{19} \tag{corr. $2^{-16}$}
\end{align*}

\newcommand{\printstate}[1]{
  \ifsubstates \pgfmathsetmacro{\roundsep}{1.25}
  \else        \pgfmathsetmacro{\roundsep}{0.80} \fi
  \pgfmathsetmacro{\opoffset}{.1}

@@

    \foreach \w in {0,...,4} {
      \ifthenelse{\equal{\w}{\r}}{
        \draw (W\rprev\w) -- (xnd\r);
        \draw (lll\r) -- (W\r\w);
      }{
        \draw (W\rprev\w) -- (W\r\w);
      }
    }
  }
}

\begin{figure}
  \substatesfalse
  % \substatesfalse to label state words and/or masks
  \centering
  \begin{tikzpicture}[xscale=1.0,yscale=1.5]%{{{
    \printstate{}
  \end{tikzpicture}%}}}
  \caption{\cipher{MiniMorus} state update function (1 step = 5 rounds).}
  \label{fig:minimorus}
\end{figure}

\begin{figure}
  \substatesfalse
  % \substatesfalse to label state words and/or masks
  \centering
  \begin{tikzpicture}[xscale=1.0,yscale=1.5]%{{{
    \printstate{}

    \draw[very thick, green!50!black]
      (C) -- (lll-1)
      (lll-1) -- (tlll-1) (lll-1) -- (xor-1) (xor-1) -- (xnd-1)
      (xnd-1) -- (and-1) (xor-1) -- (txor-1) (txor-1) -- (tanB0) (tanB0) --
      (tanB0-|and0.east)
      (and0) -- (xnd0) (xnd0) -- (tlll-1) (xnd0) -- (xor0)
      (and-1.east|-tanA-1) -- (tanA-1)
      (tanA-1) -- (txor0) (txor0) -- (xor0)
      (xor0) -- (lll0) (lll0) -- (W40)
      ;

  \end{tikzpicture}%}}}
  \caption{\cipher{MiniMorus} linear approximation fragments.}
  \label{fig:minimorus}
\end{figure}
\end{document}
